---
title: "excersise 6.3"
author: "Aser Gebremariam"
date: "2025-03-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

One interesting tip I found from the RStudio Tips account is about the DataEditR package. Manual data entry and editing in R can be tedious, especially for users who are more comfortable with a GUI-based approach. DataEditR provides an interactive way to view, enter, filter, and edit data using a Shiny-based interface.

Practicing with DataEditR
To get started, I installed the package:
  
```{r}
install.packages("DataEditR")

```
```{r}
library(devtools)
install_github("DillonHammill/DataEditR")
devtools::install_github("DillonHammill/rhandsontable")

```

Then, I experimented with data_edit(), which provides an interactive interface for editing data. I tested it using the built-in mtcars dataset:

This allowed me to modify the dataset directly in a graphical table, similar to working in Excel. The changes were saved as a new file, making data cleaning and transformation much easier.

2.Common Mistakes Reported by RStudio Diagnostics:

RStudio's diagnostics engine helps identify potential issues in your code. Common mistakes it reports include:

Function Argument Issues:

Missing Arguments: When a function call lacks required arguments.
Unmatched Arguments: When provided arguments don't match the function's parameters.
Partially Matched Arguments: When argument names are abbreviated ambiguously.
Excess Arguments: When too many arguments are supplied to a function.
Undefined Variables:

Using variables that haven't been defined in the current or parent scope.
Unused Variables:

Defining variables that are never utilized in the code.
Style Issues:

Violations of coding style guidelines, such as improper whitespace usage.

